Multiple Sclerosis Diagnosis from Natural Language Processing of Patient Text Data

### 2022-09-13 paper.tex
Added results table

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subcaption}

@@

@@

  \caption{Word Clouds For Different Parts Of The Dataset}

@@

\indent In addition to generating the word clouds for the dataset, we decided to count the average number of tokens per comment for each part of the dataset. The results of this investigation are shown in Table ****. We observe that the average number of tokens is the greatest for the diabetes control group, lower for the MS-diagnosed control group and lowest for the generic social media control group. Since sentence length varies significantly across the dataset, we need to ensure that the classifiers we train on the dataset do not rely only on the length of the comment for text classification. The implications of this difference are further discussed in the next section.

@@

\caption{Average number of tokens per comment for evry part of the dataset}
\label{tab:}

@@

\indent \textbf{K-Nearest Neighbours (KNN).} For the KNN classifier, we set the value k to 1, 2, 3, 5, 8, 10, and 100. The best accuracy was then recorded in Table ***. \\
\indent \textbf{Neural Network.} We decided to investigate both a single-layer neural network and two-layer neural network. We set the number of epochs to 10 and batch size to 64. In the final layer, we use the sigmoid activation function, and for non-output layers, we tried both the ReLU and tanh activation function. For the two-layer neural network, we set the number of neurons in the hidden layer to 50, 100 and 200. After testing these hyperparameters, the best accuracy was then recorded in Table ****. \\
\indent \textbf{Recurrent Neural Network (RNN).} Since we need an embedding for each word for the RNN, BoW and tfidf-weighted BoW cannot be used for this model. Furthermore, the RNN, by nature of being a sequential model, exemplifies the difference between input sequence lengths. Since we know that the average comment length varies considerably in different sections of the dataset, as shown in Table **** in Section ****, for RNNs we particularly need to make sure that the classifier does not rely only on the length of the text for classification. Therefore, we set the number of RNN units to minimum of the average comment lengths of the datasets in question (rounded up). Accordingly, from the values in Table **** in Section ****, we set the number of RNN units for diagnosed users vs. control one (generic) to be 15 and diagnosed users vs. control two (diabetes) to 30. Then, any comments with longer lengths were truncated to the number of RNN units. This strategy ensures that the classifier relies on the content of the text rather than its length. Lastly, we set the number of epochs to 10 and batch size to 64 before training. \\

@@

\indent The results for each of these classification models are reported in Table ****. \\
****Tables \\

>>>>

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array}
\usepackage{multirow}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

@@

\label{sec:dataanalysis}

@@

  \caption{Word Clouds For Each Part of the Dataset}

@@

\indent In addition to generating the word clouds for the dataset, we decided to count the average number of tokens per comment for each part of the dataset. The results of this investigation are shown in \autoref{tab:avglengths}. We observe that the average number of tokens is the greatest for the diabetes control group, lower for the MS-diagnosed control group and lowest for the generic social media control group. Since sentence length varies significantly across the dataset, we need to ensure that the classifiers we train on the dataset do not rely only on the length of the comment for text classification. The implications of this difference are further discussed in the next section.

@@

\caption{Average number of tokens per comment for every part of the dataset}
\label{tab:avglengths}

@@

\indent \textbf{K-Nearest Neighbours (KNN).} For the KNN classifier, we set the value k to 1, 2, 3, 5, 8, 10, and 100. The best accuracy was then recorded in \autoref{tab:results}. \\
\indent \textbf{Neural Network.} We decided to investigate both a single-layer neural network and two-layer neural network. We set the number of epochs to 10 and batch size to 64. In the final layer, we use the sigmoid activation function, and for non-output layers, we tried both the ReLU and tanh activation function. For the two-layer neural network, we set the number of neurons in the hidden layer to 50, 100 and 200. After testing these hyperparameters, the best accuracy was then recorded in \autoref{tab:results}. \\
\indent \textbf{Recurrent Neural Network (RNN).} Since we need an embedding for each word for the RNN, BoW and tfidf-weighted BoW cannot be used for this model. Furthermore, the RNN, by nature of being a sequential model, exemplifies the difference between input sequence lengths. Since we know that the average comment length varies considerably in different sections of the dataset, as shown in Table \ref{tab:avglengths} of \autoref{sec:dataanalysis}, for RNNs we particularly need to make sure that the classifier does not rely only on the length of the text for classification. Therefore, we set the number of RNN units to minimum of the average comment lengths of the datasets in question (rounded up). Accordingly, from the values in \autoref{tab:avglengths} of \autoref{sec:dataanalysis}, we set the number of RNN units for diagnosed users vs. control one (generic) to be 15 and diagnosed users vs. control two (diabetes) to 30. Then, any comments with longer lengths were truncated to the number of RNN units. This strategy ensures that the classifier relies on the content of the text rather than its length. Lastly, we set the number of epochs to 10 and batch size to 64 before training. \\

@@

\indent The results for each of these classification models are reported in \autoref{tab:results}. \\
\begin{table*}
\begin{tabular}{p{0.12\linewidth}p{0.1\linewidth}p{0.05\linewidth}p{0.1\linewidth}p{0.12\linewidth}p{0.05\linewidth}p{0.1\linewidth}p{0.1\linewidth}}
\hline\hline
 & & \multicolumn{3}{C{0.25\linewidth}}{\textbf{MS-Diagnosed vs. Control One (Generic)}} & \multicolumn{3}{C{0.25\linewidth}}{\textbf{MS-Diagnosed vs. Control Two (Diabetes)}}\\
 & & BoW & tfidf-BoW & Embeddings &  BoW & tfidf-BoW & Embeddings\\
\multirow{3}{\linewidth}{\textbf{Logistic Regression}} & Precision & 96.3 & 95.2	& 90.5 & 90.3 & 90.2 & 87.4\\
 & Accuracy & 92.9 & 93.3 & 91.8 & 91.3 & 91.7 & 86.4 \\
 & Recall & 90.5 & 92.0 & 93.3 & 92.5 & 93.4 & 86.3 \\
\multirow{3}{\linewidth}{\textbf{Naïve Bayes}} & Precision & 88.6 & 89.2 & 85.4 & 93.4 & 93.8 & 86.8\\
 & Accuracy & 91.0 & 91.6 & 87.5 & 92.0 & 92.4 & 77.2\\
 & Recall & 93.6 & 94.2 & 89.7 & 91.2 & 91.6 & 73.5\\
\multirow{3}{\linewidth}{\textbf{KNN}} & Precision & 70.8	& 66.6 & 85.0 & 71.5 & 83.0 & 94.6\\
 & Accuracy & 83.5 & 78.3 & 87.1 & 77.3 & 85.1 & 77.8\\
 & Recall & 96.1 & 88.1 & 89.2 & 81.3 & 87.2 & 71.4\\
\multirow{3}{\linewidth}{\textbf{1-Layer Neural Network}} & Precision & 94.2 & 92.4 & 94.8 & 92.3 & 90.9 & 91.5\\
 & Accuracy & 92.3 & 92.6 & 93.9 & 91.5 & 90.8 & 89.8\\
 & Recall & 91.2 & 93.2 & 93.4 & 91.1 & 91.2 & 88.9\\
\multirow{3}{\linewidth}{\textbf{2-Layer Neural Network}} & Precision & 94.1 & 95.0 & 95.8 & 90.2 & 90.6 & 88.7\\
 & Accuracy & 92.9 & 93.3 & 94.3 & 90.8 & 91.6 & 90.1\\
 & Recall & 92.3 & 92.2 & 93.2 & 91.7 & 92.9 & 91.7\\
\multirow{3}{\linewidth}{\textbf{RNN}} & Precision & N/A & N/A & 80.2 & N/A & N/A & 84.9\\
 & Accuracy & N/A & N/A & 86.7 & N/A & N/A & 88.7\\
 & Recall & N/A & N/A & 92.8 & N/A & N/A & 92.4\\
\multirow{3}{\linewidth}{\textbf{LSTM}} & Precision & N/A & N/A & 94.1 & N/A & N/A & 88.7\\
 & Accuracy & N/A & N/A & 94.1 & N/A & N/A & 90.8\\
 & Recall & N/A & N/A & 94.4 & N/A & N/A & 92.2\\
\hline\hline
\caption{Results for all the classification models}
\label{tab:results}
\end{table*}
